First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-08-03 ms.tex
Added back in omitted words
Adding error plot and corresponding description in the paper.

@@

We demonstrate the impact of our diffuse model again by running the golden data set 
through our entire analysis pipeline with and without using the diffuse model. Because the 
foreground models used for calibration in the two runs are identical (diffuse is omitted for 
calibration), the calibration solutions were identical and therefore the dirty power spectra 
were identical as well. We compare the model and residual power spectra by direct 
subtraction in Figure~\ref{fig:diffuse_diff}. 
The top panel shows \textbf{our foreground model power spectrum
minus the model power spectrum when including diffuse}. 
Because our diffuse model added power to the full foreground model, the entire plot is
negative (red).
Even the EoR window is red (albeit at a much lower level than the wedge) because of power
leakage from non-uniform spectral sampling and from the dynamic range limit of the 
Blackman-Harris window function.
The bottom panel is the difference in residual 
power. The wedge is completely positive (blue), indicating that the diffuse model 
successfully subtracted from the dirty visibilities. The differences in the window are positive 
and negative, indicating that 
the differences in the foreground model in this region are below the three hour noise level.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{example_2derror.pdf}
\caption{
\textbf{
Error level corresponding to Figure~\ref{fig:example_ps}. The noise is relatively low at
short baseline length (low $k_{\perp}$) due to the dense MWA core. The array is more
sparse at longer baselines, and the noise increases. The second $k_{||}$ bin has slightly
lower noise than the rest of the $k_{||}$ modes due to the interaction between the
Lomb-Scargle periodogram with the Blackman-Harris window function applied to the data.
}
\label{fig:example_2derror}
}
\end{center}
\end{figure}

\textbf{Figure~\ref{fig:example_2derror} shows the error level corresponding to the two 
dimensional power spectrum in Figure~\ref{fig:example_ps}. These errors
are found by propagating noise measured from calibrated visibilities through the entire
pipeline. The dense core of the MWA results in relatively low noise at low $k_\perp$.
As the $(u,v)$ density of the array decreases at longer baselines, the noise increases.
The noise is mostly constant across $k_{||}$ because the Fourier transform distributes
the noise in frequency to all modes equally \citep{Morales:2004}.
The exception is the second $k_{||}$ bin, which has slightly lower noise than the rest of the 
$k_{||}$ modes. This is a result of the Lomb-Scargle periodogram interacting with the
Blackman-Harris window function we apply to the data. In the case of $k_{||}=0$
(shown as the bottom bin on the log plot), the
cosine term carries all the information and has a noise level $\sqrt{2}$ lower than any other
sine or cosine term individually. The first non-zero $k_{||}$ mode is highly covariant with the 
bottom bin due to the window function. Therefore the noise on this mode's cosine term is 
lower than other higher order cosines. With the added contribution from the sine term, this
mode contains the lowest level of noise.
}

@@

We demonstrate the impact of our diffuse model again by running the golden data set 
through our entire analysis pipeline with and without using the diffuse model. Because the 
foreground models used for calibration in the two runs are identical (diffuse is omitted for 
calibration), the calibration solutions were identical and therefore the dirty power spectra 
were identical as well. We compare the model and residual power spectra by direct 
subtraction in Figure~\ref{fig:diffuse_diff}. 
The top panel shows \textbf{our point source foreground model power spectrum
minus the model power spectrum when including diffuse}. 
Because our diffuse model added power to the full foreground model, the entire plot is
negative (red).
Even the EoR window is red (albeit at a much lower level than the wedge) because of power
leakage from non-uniform spectral sampling and from the dynamic range limit of the 
Blackman-Harris window function.
The bottom panel is the difference in residual 
power. The wedge is completely positive (blue), indicating that the diffuse model 
successfully subtracted from the dirty visibilities. The differences in the window are positive 
and negative, indicating that 
the differences in the foreground model in this region are below the three hour noise level.
